Our project is to develop an obstacle-detection system for use by an autonomous sailboat.  The UBC Sailbot team is developing this sailbot to cross the Atlantic Ocean as part of the Microtransat challenge.  Our system must detect a wide range of hazards, including boats, nets, and floating debris, with sufficient range and precision to avoid them.  After researching a variety of detection systems, we propose a combination of IR imaging and satellite tracking.  These systems should allow detection of all anticipated categories of obstacles, while meeting the size, power, and mounting constraints of the sailbot.




Add to background- info on what the challenge is, what  happened to previous attempts, what Sailbot is and their projects. Condense all this here

IR testing + pictures from the results, showing that Hey guess what we have access to an IR camera. Put pictures in the software section

SAR is a bonus objective, totally not needed but would be nice to have. Downgrade other options (remove passive acoustic)

Focus technical background on methods we'll use, move others to Alternatives.

Fill out Software and Testing

AIS and SAR defined earlier- in technical background. By the time they finish the background, there should be no questions as to what each system is/ how it works.

fill out executive summary. it sucks, we all know it sucks.

would LIDAR actually work? Really move it to Alternatives, since its now outside of both our power and price ranges.

Move details out of Project objectives, just have summaries there.

lost fishing nets (abandoned marine debris) is not worth the effort. Too rare. The ocean is big, we are small.

Make it clear that we aren't doing avoidance, only detection. Early on.

Existing Solutions section isn't meant for what Sailbots' done- it's meant for what outside solutions are there.

Existing Solutions and State of the Art Commercial Systems could potentially be merged. What's the difference?

Background: say what we need to detect, why, and what we don't need to detect (dont need is currently in Objectives)

Actually, a lot of Objectives needs to be condensed and put earlier (background?)

Need to test IR at sunset (looking to the west, right into the sun)

