\begin{thebibliography}{99}

% organize alphabetically by author's last name or company name

\bibitem{AMN} Elkins, L., Sellers, D., \& Monach, W.R. (2010). \textit{The Autonomous Maritime Navigation (AMN) Project: Field Tests, Autonomous and Cooperative Behaviors, Data Fusion, Sensors, and Vehicles}. Retrieved from http://onlinelibrary.wiley.com/doi/10.1002/rob.20367/pdf

\bibitem{coplien-tdd-waste} Coplien, J.O. \textit{Why Most Unit Testing is Waste}. Retrieved November 19, 2014 from http://www.rbcs-us.com/documents/Why-Most-Unit-Testing-is-Waste.pdf

\bibitem{flir-md324} Flir. (2014). \textit{FLIR MD-Series Thermal Imager}. Retrieved from http://www.flir.com/cvs/americas/en/maritime/view/?id=59356\&collectionid=1129\&col=59377

\bibitem{furuno__marine-radar-guide} Furuno. (2008). \textit{Operator's Guide to Marine Radar}. Retrieved from http://www.getfeetwet.com/FurunoRadarGuide-LR.pdf

\bibitem{gam-electronics__ss-2} GAM Electronics. (2014). \textit{SS-2 Mini VHF Antenna}. Retrieved from http://gamelectronicsinc.com/product/ss-2/

\bibitem{gpsd__overview}. GPSD Project. \textit{About GPSD}. Retrieved November 27, 2014, from http://www.catb.org/gpsd/

\bibitem{SAR-manual} Jackson, C.R., \& Apel, J.R. \textit{SAR Users Manual}. Retrieved from http://www.sarusersmanual.com

\bibitem{Mace} Mace,T. (2011). \textit{At-sea detection of marine debris: Overview of technologies, processes, issues, and options}. Marine Pollution Bulletin. doi: 10.1016/j.marpolbul.2011.08.042

\bibitem{transat-history} Microtransat Challenge. (2014). \textit{History of the Microtransat Challenge}. Retrieved from http://www.microtransat.org/history.php

\bibitem{transat__w-e_start-finish} Microtransat Challenge. (2014). \textit{West to East Route Start and Finish Lines}. Retrieved from http://www.microtransat.org/tracking/westeast.html

\bibitem{nmea__standards} National Marine Electronics Association (NMEA). \textit{Standards (NMEA 2000, 0183)}. Retrieved November 27, 2014, from http://www.nmea.org/content/nmea\_standards/nmea\_standards.asp

\bibitem{ODU-boat-IR-detection} Old Dominion University Vision Lab. (2009). \textit{Small Boat Detection for Port Security Applications}. Retrieved from http://eng.odu.edu/visionlab/research/boat.php

\bibitem{optotherm-emisstable} Optotherm Thermal Imaging. (2014). \textit{Emissivity Tables}. Retrieved from http://www.optotherm.com/emiss-table.htm

\bibitem{provost-tdd} Provost, P. (September 2013). \textit{What Really Matters in Developer Testing}. Retrieved from http://www.peterprovost.org/blog/2013/09/23/what-really-matters-in-developer-testing/

\bibitem{raymarine-eseries} Raymarine by FLIR. (2014). \textit{Raymarine Marine Radome} Retrieved from http://www.raymarine.com/view/?id=2966\&collectionid=96\&col=3021

\bibitem{tech-info} UBC Engineering Physics Project Lab. (2014). \textit{Technical Info 2013}. Retrieved from docs.google.com/document/d/\\1WU\_duqr20lqg48ukjsuhUJPJhsSNkrWiEVf3uU4xS0A/pub\#h.f2e6v0ormnoc

\bibitem{ubc-sailbot__image} UBC Sailbot Team. (2014). \textit{Why We Do This}. Retrieved from http://ubcsailbot.org/

\bibitem{us-ais-requirements} United States Coast Guard. \textit{AIS REQUIREMENTS}. Retrieved November 27, 2014 from http://www.navcen.uscg.gov/?pageName=AISCarriageReqmts

\bibitem{velodyne-vlp16} Velodyne High Definition Lidar. (2014). \textit{Velodyne VLP-16}. Retrieved from http://www.velodynelidar.com/lidar/hdlproducts/vlp16.aspx

\bibitem{weatherdock__easyais-025} WeatherDock. (2014). \textit{EasyAis 025}. Retrieved from http://www.easyais.com/en/products/easyais-a025/

\bibitem{marine-traffic} MarineTraffic. (2014). \textit{AIS Traffic and Locations}. Retrieved from https://www.marinetraffic.com/

\end{thebibliography}