\begin{thebibliography}{9999999999999999999999999999}

% organize alphabetically by author's last name or company name

\bibitem{AMN} The Autonomous Maritime Navigation (AMN) Project:
Field Tests, Autonomous and Cooperative Behaviors,
Data Fusion, Sensors, and Vehicles. (2010). Retrieved from http://onlinelibrary.wiley.com/doi/10.1002/rob.20367/pdf

\bibitem{optotherm-emisstable} Optotherm Thermal Imaging. (2014). \textit{Emissivity Tables}. Retrieved from http://www.optotherm.com/emiss-table.htm

\bibitem{raymarine-eseries} Raymarine by FLIR Marine Radome. (2014). Retrieved from http://www.raymarine.com/view/?id\=2966\&collectionid\=96\&col\=3021

\bibitem{tech-info} UBC Engineering Physics Project Lab Task Description. (2014) \textit{Technical Info 2013}. Retrieved from docs.google.com/document/d/\\1WU\_duqr20lqg48ukjsuhUJPJhsSNkrWiEVf3uU4xS0A/pub\#h.f2e6v0ormnoc

\bibitem{velodyne-vlp16} Velodyne High Definition Lidar. (2014). Retrieved from http://www.velodynelidar.com/lidar/hdlproducts/vlp16.aspx

\bibitem{transat-history} History of the Microtransat Challenge. (2014). Retrieved from http://www.microtransat.org/history.php

\bibitem{ODU-boat-IR-detection} Small Boat Detection for Port Security Applications. (2009). Retrieved from http://eng.odu.edu/visionlab/research/boat.php

\bibitem{Mace} Mace,T. At-sea detection of marine debris: Overview of technologies, processes, issues, and options. (2011). Marine Pollution Bulletin. doi: 10.1016/j.marpolbul.2011.08.042

\bibitem{SAR-manual} SAR Users Manual. Retrieved from http://www.sarusersmanual.com

\end{thebibliography}