% This is a subsection: use only subsubsections in this file.

\iffalse
This is a direct follow-up from the details contained in the Project Proposal section. The list can describe the final state of each item in the list, any differences between the original deliverables and the actual deliverables, and in what form the Project Sponsor can expect to receive the Deliverable from the Team Members.
\fi

Throughout the past three months, the scope of our project has changed. Our deliverables are grouped according to those that will be handed off to the sponsor at the end of term (Section \ref{sec:projectdeliverables:listofdeliverables:currentdeliverables}) and those that were initially planned but either scrapped or are ongoing at the time of this report (Section \ref{sec:projectdeliverables:listofdeliverables:formerdeliverables}) and not included in the project completion report.

\subsubsection{\label{sec:projectdeliverables:listofdeliverables:currentdeliverables}Current Deliverables}

\begin{description}
\item[Test Rig hardware 2.0] The second design of a plastic waterproof housing, with waterjet-cut internal plastic supports and mounting structure. A 3D-printed housing secures the FLIR Lepton infrared camera and breakout board, and the internal mounting structure supports this part as well as a Raspberry Pi computer, a rechargeable battery pack, an inertial motion unit (IMU), and a button to start and stop recording. The Test Rig can be clamped to a tripod. Pieces of the test rig (particularly the 3D-printed camera mount) will serve as a model for the final housing of the infrared camera.
\item[Test Rig software] The Test Rig software records IMU data and infrared images at about 20 frames per second, and allows this data to be viewed and transferred wirelessly from the Test Rig hardware. The software is written in Python and C++ and is synchronized to a GitHub repository; it was developed in conjunction with the Sailbot Obstacle Avoidance team.
\item[Support equipment] We obtained an IMU and two battery packs for the Sailbot team to use with the Test Rig and in the final obstacle detection system.
\end{description}

\subsubsection{\label{sec:projectdeliverables:listofdeliverables:formerdeliverables}Former Deliverables}

\begin{description}
\item[AIS signal processor (receiver, connectors, software library)] \hfill
\begin{itemize}
\item written in Python
\item interpret data from AIS receiver
\item report position and speed of nearby vessels to Sailbot navigation software
\end{itemize}
Responsibility for this item was taken over by the Sailbot Electrical team.

\item[IR signal processor (camera, connectors, software library)] \hfill
\begin{itemize}
\item written in Python
\item capture IR images ahead of Sailbot
\item detect and track features in image
\item determine position and speed of features in image
\item report position and speed of detected objects to Sailbot navigation software
\end{itemize}
The pieces of this task that have been completed are outlined in Section \ref{sec:projectdeliverables:listofdeliverables:formerdeliverables}. The image analysis code is still in development in part by us (see Section \ref{sec:projectdeliverables:ongoingcommitments}) and in part by the Sailbot Obstacle Avoidance team.

\item[Report on performance characteristics for all systems] \hfill
\begin{itemize}
\item detection distance
\item detection likelihood
\item best weather conditions for operating
\item power draw
\item input data required from Sailbot sensors
\item frequency of data output
\end{itemize}
As the image analysis code is incomplete, and the final infrared camera has not been chosen, this item will not be completed.
\end{description}
