\begin{thebibliography}{99}
\raggedright

% organize alphabetically by author's last name or company name

\bibitem{AMN} Elkins, L., Sellers, D., \& Monach, W.R. (2010). \textit{The Autonomous Maritime Navigation (AMN) Project: Field Tests, Autonomous and Cooperative Behaviors, Data Fusion, Sensors, and Vehicles}. Retrieved from http://onlinelibrary.wiley.com/doi/10.1002/rob.20367/pdf

\bibitem{coplien-tdd-waste} Coplien, J.O. \textit{Why Most Unit Testing is Waste}. Retrieved November 19, 2014 from http://www.rbcs-us.com/documents/Why-Most-Unit-Testing-is-Waste.pdf

\bibitem{port-technology__global-turnaround-times} Ducruet, C., \& Merk, O. (2013, September). Examining container vessel turnaround times across the world. \textit{Port Technology International}, 19-20.

\bibitem{flir-md324} Flir. (2014). \textit{FLIR MD-Series Thermal Imager}. Retrieved from http://www.flir.com/cvs/americas/en/maritime/view/?id=59356\&collectionid=1129\&col=59377

\bibitem{furuno__marine-radar-guide} Furuno. (2008). \textit{Operator's Guide to Marine Radar}. Retrieved from http://www.getfeetwet.com/FurunoRadarGuide-LR.pdf

\bibitem{gam-electronics__ss-2} GAM Electronics. (2014). \textit{SS-2 Mini VHF Antenna}. Retrieved from http://gamelectronicsinc.com/product/ss-2/

\bibitem{gpsd__overview} GPSD Project. \textit{About GPSD}. Retrieved November 27, 2014, from http://www.catb.org/gpsd/

\bibitem{SAR-manual} Jackson, C.R., \& Apel, J.R. \textit{SAR Users Manual}. Retrieved from http://www.sarusersmanual.com

\bibitem{jallal__how-many-ships} Jallal, Craig. (July 31, 2012). \textit{How Many Ships Are There in the World?} Retrieved from http://shippingresearch.wordpress.com/2012/07/31/how-many-ships-are-there-in-the-world/

\bibitem{kaehler__learning-opencv} Kaehler, Adrian, \& Bradski, Gary. (October 2013). \textit{Learning OpenCV: Computer Vision in C++ with the OpenCV Library}. O'Reilly Media.

\bibitem{Mace} Mace, T. (2011). \textit{At-sea detection of marine debris: Overview of technologies, processes, issues, and options}. Marine Pollution Bulletin. doi: 10.1016/j.marpolbul.2011.08.042

\bibitem{maersk__triple-e-class} Maersk. (2014). \textit{Triple-E Vessels}. Retrieved from http://www.maersktechnology.com/stories/stories/pages/triple-evessels.aspx

\bibitem{marine-traffic} Marine Traffic. (2014). \textit{AIS Traffic and Locations}. Retrieved from https://www.marinetraffic.com/

\bibitem{mca-uk__mgn324} Maritime and Coastguard Agency - UK. (September 14, 2006). \textit{Maritime Guidance Note (MGN) 324}. Retrieved from https://mcanet.mcga.gov.uk/public/c4/solasv/m\_notice/mgn/mgn324.pdf

\bibitem{milltech__amec-cypho150} Milltech Marine. \textit{AMEC CYPHO-150 AIS Receiver}. Retrieved December 29, 2014 from http://www.milltechmarine.com/AMEC-CYPHO-150-AIS-Receiver\_p\_263.html

\bibitem{transat-history} Microtransat Challenge. (2014). \textit{History of the Microtransat Challenge}. Retrieved from http://www.microtransat.org/history.php

\bibitem{transat__w-e_start-finish} Microtransat Challenge. (2014). \textit{West to East Route Start and Finish Lines}. Retrieved from http://www.microtransat.org/tracking/westeast.html

\bibitem{natgeo__iceberg-frequency} National Geographic. (2008). \textit{Iceberg Frequency in April}. Retrieved from http://education.nationalgeographic.com/education/photo/icechart-frequency/?ar\_a=1

\bibitem{nmea__standards} National Marine Electronics Association (NMEA). \textit{Standards (NMEA 2000, 0183)}. Retrieved November 27, 2014, from http://www.nmea.org/content/nmea\_standards/nmea\_standards.asp

\bibitem{ODU-boat-IR-detection} Old Dominion University Vision Lab. (2009). \textit{Small Boat Detection for Port Security Applications}. Retrieved from http://eng.odu.edu/visionlab/research/boat.php

\bibitem{optotherm-emisstable} Optotherm Thermal Imaging. (2014). \textit{Emissivity Tables}. Retrieved from http://www.optotherm.com/emiss-table.htm

\bibitem{pure-eng} Pure Engineering. \textit{Lepton}. Retrieved from http://www.pureengineering.com/projects/lepton

\bibitem{provost-tdd} Provost, P. (September 2013). \textit{What Really Matters in Developer Testing}. Retrieved from http://www.peterprovost.org/blog/2013/09/23/what-really-matters-in-developer-testing/

\bibitem{raymarine-eseries} Raymarine by FLIR. (2014). \textit{Raymarine Marine Radome} Retrieved from http://www.raymarine.com/view/?id=2966\&collectionid=96\&col=3021

\bibitem{rpi} Raspberry Pi Foundation. (2015). Retrieved from http://www.raspberrypi.org/

\bibitem{tech-info} UBC Engineering Physics Project Lab. (2014). \textit{Technical Info 2013}. Retrieved from docs.google.com/document/d/\\1WU\_duqr20lqg48ukjsuhUJPJhsSNkrWiEVf3uU4xS0A/pub\#h.f2e6v0ormnoc

\bibitem{ubc-sailbot__image} UBC Sailbot Team. (2014). \textit{Why We Do This}. Retrieved from http://ubcsailbot.org/

\bibitem{us-ais-requirements} United States Coast Guard. \textit{AIS REQUIREMENTS}. Retrieved November 27, 2014 from http://www.navcen.uscg.gov/?pageName=AISCarriageReqmts

\bibitem{velodyne-vlp16} Velodyne High Definition Lidar. (2014). \textit{Velodyne VLP-16}. Retrieved from http://www.velodynelidar.com/lidar/hdlproducts/vlp16.aspx

\bibitem{weatherdock__easyais-025} WeatherDock. (2014). \textit{EasyAis 025}. Retrieved from http://www.easyais.com/en/products/easyais-a025/

\bibitem{worldatlas__atlantic-ocean} WorldAtlas. (2014). \textit{Atlantic Ocean Details}. Retrieved from http://www.worldatlas.com/aatlas/infopage/oceans/atlanticocean.htm

\bibitem{detection-offroad} Manduchi, R. et al. (2005). \textit{Obstacle Detection and Terrain Classification for Autonomous Off-Road Navigation}. Retrieved from http://link.springer.com/article/10.1023/B:AURO.0000047286.62481.1d

\bibitem{optical-flow-detection} Mallot, Hanspeter A. et al. (1991). \textit{Inverse perspective mapping simplifies optical flow computation and obstacle detection}. Journal of Biological Cybernetics. Retrieved from http://link.springer.com/article/10.1007/BF00201978

\bibitem{unmanned-ground-vehicles} Matthies, L. et al. (1996). \textit{Obstacle Detection for Unmanned Ground Vehicles: A Progress Report}. Robotics Research. Retrieved from http://link.springer.com/chapter/10.1007/978-1-4471-0765-1\_52

\bibitem{ASV-sonar} Heidarsson, H. \& Sukhatme, G. (2011). \textit{Obstacle Detection and Avoidance for an Autonomour Surface Vehicle using a Profiling Sonar}. Retrieved from http://robotics.usc.edu/publications/media/uploads/pubs/693.pdf


\end{thebibliography}